\thesistitle

### 2019-07-18 main.tex
Better formulas
Better math
Clone types summarized
Improved type 1 clones shortcomings section
AST Filtering
Separated stuff
Moved related work from paper to thesis
Better table (now it fits :diamond_shape_with_a_dot_inside:)
Testing listings

\documentclass[a4paper,10pt,titlepage]{report}
%%This template is based on Paco van Beckhoven's thesis.

\usepackage{xspace}
\usepackage{xargs}   % Use more than one optional parameter in a new commands
\usepackage{xcolor}

@@

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{titlepic}
\usepackage{vhistory}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[backend=bibtex, style=ieee,citestyle=numeric-comp]{biblatex}
\usepackage[colorinlistoftodos, prependcaption]{todonotes}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{cmap}
\usepackage{float}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage{microtype}

\usepackage{titlesec}

@@

\renewcommand{\maketitle}{%
	% The cover page
	% --------------
	\thispagestyle{empty}
	\enlargethispage{30pt}
	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
	% Will be page 0, s.t. contents start on page 1
	\setcounter{page}{0}
	% \eccoverhead
	% Volume and article title, author(s)
	\vspace{60pt}
	\begin{center}
		{\Huge\bfseries Towards Automated Refactoring of Code Clones \par}
		% Earlier versions:
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Source Code Analysis
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting test suite effectiveness using static analysis
		\vspace{44pt}
		{\Large\bfseries Simon Baars \par}
		\email{simon.mailadres@gmail.com}\\
		\vspace{11pt}
		30 June 2019, \pageref{LastPage} pages
	\end{center}
	\vfill
	\begin{tabular}{ll}
		\textbf{Research supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
		\textbf{Host/Daily supervisor:} Xander Schrijen, \email{x.schrijen@sig.eu}\\
		\textbf{Host organisation/Research group:} Software Improvement Group (SIG), \url{http://sig.eu/}
	\end{tabular}
	\uvacoverfoot
	\newpage
	\setcounter{footnote}{0}
	\renewcommand{\thefootnote}{\arabic{footnote}}
	\setlength{\parskip}{0pt}
}

@@

\maketitle
\input{sections/abstract}
\tableofcontents
\input{sections/introduction}
\input{sections/background}
\input{sections/research}
\input{sections/results}
\input{sections/discussion}
\input{sections/related_work}
\input{sections/conclusion}
\input{sections/acknowledgements}

\printbibliography[heading=bibintoc]
\printglossaries%

>>>>

\documentclass[a4paper,10pt,titlepage]{report}

\usepackage{xspace}
\usepackage{xargs}   % Use more than one optional parameter in a new commands
\usepackage[table,xcdraw]{xcolor}

@@

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{titlepic}
\usepackage{vhistory}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[backend=bibtex, style=ieee,citestyle=numeric-comp]{biblatex}
\usepackage[colorinlistoftodos, prependcaption]{todonotes}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{cmap}
\usepackage{float}
\usepackage{hyperref}
\usepackage{wrapfig}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{blue}{rgb}{0,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\newfloat{eqfloat}{h}{eqflts}
\floatname{eqfloat}{Equation}

@@

\renewcommand{\maketitle}{%
	% The cover page
	% --------------
	\thispagestyle{empty}
	\enlargethispage{30pt}
	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
	% Will be page 0, s.t. contents start on page 1
	\setcounter{page}{0}
	% \eccoverhead
	% Volume and article title, author(s)
	\vspace{60pt}
	\begin{center}
		{\Huge\bfseries Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages \par}
		% Earlier versions:
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Source Code Analysis
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting test suite effectiveness using static analysis
		\vspace{44pt}
		{\Large\bfseries Simon Baars \par}
		\email{simon.mailadres@gmail.com}\\
		\vspace{11pt}
		30 June 2019, \pageref{LastPage} pages
	\end{center}
	\vfill
	\begin{tabular}{ll}
		\textbf{Research supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
		\textbf{Host/Daily supervisor:} Xander Schrijen, \email{x.schrijen@sig.eu}\\
		\textbf{Host organisation/Research group:} Software Improvement Group (SIG), \url{http://sig.eu/}
	\end{tabular}
	\uvacoverfoot
	\newpage
	\setcounter{footnote}{0}
	\renewcommand{\thefootnote}{\arabic{footnote}}
	\setlength{\parskip}{0pt}
}

@@

\maketitle
\input{sections/abstract}
\tableofcontents
\input{sections/introduction}
\input{sections/background}
\input{sections/related_work}
\input{sections/research}
\input{sections/clonerefactor}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}
\input{sections/acknowledgements}

\printbibliography[heading=bibintoc]
\printglossaries
